cardinalR: Generating interesting high-dimensional data structures

### 2025-08-04 paper-cardinalR.Rmd
Updated installation

```r
devtools::install_github("JayaniLakshika/cardinalR")
```

@@

```{r, label = "fig-highd-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `mobiusgau` data. The helical spiral cluster is represented in dark green, the hemisphere cluster in orange, the uniform cube-shaped cluster in purple, the blunted cone cluster in pink, and the Gaussian-shaped cluster in light green."}
#| fig-width: 15
#| fig-height: 5

@@

```{r, label = "fig-nldr-layouts", fig.cap="Six different dimension reduction representations of the `mobiusgau` data using default hyperparameter settings: (a) tSNE, (b) UMAP, (c) PAHTE, (d) TriMAP, (e) PaCMAP, and (f) PCA."}

>>>>

```r
pak::pak("JayaniLakshika/cardinalR")
```

@@

```{r, label = "fig-highd-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the five clusters data. The helical spiral cluster is represented in dark green, the hemisphere cluster in orange, the uniform cube-shaped cluster in purple, the blunted cone cluster in pink, and the Gaussian-shaped cluster in light green."}
#| fig-width: 15
#| fig-height: 5

@@

```{r, label = "fig-nldr-layouts", fig.cap="Six different dimension reduction representations of the five clusters data using default hyperparameter settings: (a) tSNE, (b) UMAP, (c) PAHTE, (d) TriMAP, (e) PaCMAP, and (f) PCA."}

### 2025-08-04 paper-cardinalR.tex
Added package installation for the paper
Updated installation

\begin{verbatim}
devtools::install_github("JayaniLakshika/cardinalR")
\end{verbatim}

@@

\caption{\label{tab:odd-shape-tb-pdf}cardinalR multiple clusters generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
make\_mobiusgau & \\
make\_multigau & \\
make\_curvygau & \\
make\_threeclust01 & \\
make\_fourclust01 & \\
\addlinespace
make\_fiveclust01 & \\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-highd-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `mobiusgau` data. The helical spiral cluster is represented in dark green, the hemisphere cluster in orange, the uniform cube-shaped cluster in purple, the blunted cone cluster in pink, and the Gaussian-shaped cluster in light green.}\label{fig:fig-highd-proj}
\end{figure}

@@

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-nldr-layouts-1} \caption{Six different dimension reduction representations of the `mobiusgau` data using default hyperparameter settings: (a) tSNE, (b) UMAP, (c) PAHTE, (d) TriMAP, (e) PaCMAP, and (f) PCA.}\label{fig:fig-nldr-layouts}
\end{figure}

>>>>

\begin{verbatim}
pak::pak("JayaniLakshika/cardinalR")
\end{verbatim}

@@

\caption{\label{tab:odd-shape-tb-pdf}cardinalR multiple clusters generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
make\_mobiusgau & \\
make\_multigau & \\
make\_curvygau & \\
make\_multigrid & \\
make\_threeclust01 & \\
\addlinespace
make\_fourclust01 & \\
make\_fiveclust01 & \\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-highd-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the five clusters data. The helical spiral cluster is represented in dark green, the hemisphere cluster in orange, the uniform cube-shaped cluster in purple, the blunted cone cluster in pink, and the Gaussian-shaped cluster in light green.}\label{fig:fig-highd-proj}
\end{figure}

@@

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-nldr-layouts-1} \caption{Six different dimension reduction representations of the five clusters data using default hyperparameter settings: (a) tSNE, (b) UMAP, (c) PAHTE, (d) TriMAP, (e) PaCMAP, and (f) PCA.}\label{fig:fig-nldr-layouts}
\end{figure}
